---
title: "Modeling a vaccination campaign against monkeypox in Mexico City"
author: 
  - name: Rodrigo Zepeda-Tello
    orcid: 0000-0003-4471-5270
    email: rodrigo.zepeda@imss.gob.mx
    affiliations:
      - name: Instituto Mexicano del Seguro Social
  - name: Mayra Núñez-López 
    orcid: 0000-0002-2851-0729
    affiliations:
      - name: Instituto Tecnológico Autónomo de México
  - name: Génesis Luigi-Bravo
    orcid: 0000-0002-2079-5993
format: html
bibliography: references.bib
csl: vancouver.csl
execute: 
  fig-dpi: 750
  echo: false
  warning: false
  message: false
---

```{r}
#| echo: false
#| message: false
#| warning: false
remake_plots <- FALSE
pacman::p_load(tidyverse, ggdag, latex2exp, ggtext, lubridate, knitr, glue)
```

## Introduction

Since May 2022 the global outbreak of Monkeypox (MPX) has been reported in over 118 countries with most cases occurring among Men who have Sex with Men (MSM) [@philpott2022epidemiologic; @hadeler2012pair; @kraemer2022tracking; @liu2022monkeypox]. In Mexico, 98% of cases have been reported in men, most of these are aged 20-50 [@mpxdge]. To date 2,654 cases have been confirmed with most of them (60%) being reported in Mexico City, where the only laboratory in the country capable of testing for MPX (before October 6th) is headquartered [@indre]. As the case count continues rising, activists have demanded more testing and access to vaccines. To date the country has not implemented a vaccination campaign. 

The purpose of this document is to model the prevention opportunity of a vaccination campaign against MPX in Mexico City. 

## Methods

### Data

#### Monkeypox cases

Weekly incident cases were obtained from the reports of the General Directorate of Epidemiology of Mexico [@mpxdge].

#### Parameter information



### Mathematical model

```{r}
#| label: fig-diagram-transmission
#| message: false
#| warning: false
#| fig-height: 8.5
#| fig-width: 20
#| echo: false
#| out-width: 100%
#| fig-align: center
#| fig-cap: "Diagram of the transmission mechanics of the model. There are five different categories of individuals: Susceptible $S$, Exposed $E$, Infected $I$, Recovered $R$, and Vaccinated $V$. We assume vaccinated and recovered individuals become immune for the remaining of the modeled period. "
knitr::include_graphics("images/diagram.svg")
```

Our model is a pair-formation Susceptible-Exposed-Infected-Recovered (SEIR) system of differential equations adapted from [@betti2022pair]. Briefly, in pair formation models the infection is driven by the rate of sexual **partnership** formation between individuals and transmission probabilities per sexual encounter within the partnership [@kretzschmar2017pair; @hadeler2012pair; @hadeler1988models]. In these models, **single** individuals (individuals that don't form partnerships) don't get infected nor infect others. A sexual partnership starts when two individuals have their first sexual encounter (rate $\rho$ of partnership formation) and will continue having sexual encounters (at a rate $\phi$) until the partnership ends (rate $\sigma$ of partnership dissolution). After a partnership dissolves, individuals become single again. 

The disease is transmitted when two individuals have a sexual encounter with one of them being susceptible $S$ and the other being infected $I$. Once contagion takes place the susceptible individual becomes exposed (incubating) $E$. An exposed individual eventually evolves to an infectious individual $I$ at a rate $\theta$. Infectious individuals recover at a rate $\delta$. Recovered individuals are represented by the letter $R$. Susceptible individuals can also become vaccinated at a rate $\nu$. We assume that vaccinated $V$ and recovered $R$ individuals cannot be reinfected. 

The differential equations representation for the model and the compartmental diagram can be found in [Appendix -@sec-diffeq]. 




#### Model Fitting

We used the weekly incident cases $i_w$ of [@mpxdge] for Mexico City for each week $w$ and fitted them against the modeled incident cases for the same week. We assumed that only a fraction $p_{\text{detect}}$ of all the cases corresponded to the observed cases, $i_w$. And that the observed cases follow a Negative Binomial distribution parametrized by its mean $p_{\text{detect}}\cdot I(w)$ and precision $\tau$:

$$
i_w \sim \textrm{NegativeBinomial}\big(p_{\text{detect}}\cdot I(w), \tau\big).
$$
with

$$
\tau \sim \textrm{InverseGamma}(2,3), \quad \text{and}\quad p_{\text{detect}} \sim \textrm{Beta}(2,1).
$$

@tbl-parameters contains information regarding the priors for all parameters. Trajectories for the model were simulated via the `DifferentialEquations` package using the `Rodas4` algorithm [@rackauckas2017differentialequations]. Parameter fitting was done via No-U-Turn-Sampling (NUTS) with the `Turing` library in `Julia` version 1.8.2 [@ge2018turing; @bezanson2012julia; @hoffman2014no]. We used the $\hat{R}$ and Gelman-Rubin's test to assess convergence [@gelman1992inference]. All graphics were done in `R` version 4.2.1 (2022-06-23) using `ggplot2` [@ggplot2; @R]. 

#### Estimation of the basic reproductive number, $\mathcal{R}_0$

TBD

#### Scenario simulation

We used the simulated posterior distribution of the model's parameters to construct the baseline scenario with no vaccination $\nu = 0$. We then repeated the simulations under different vaccination rate scenarios $\{\nu_i\}$. 

### Code and data availability

Both the code for the model and the data can be found in our [Github repository](https://github.com/RodrigoZepeda/mpx)

## Results

```{r}
mparam  <- read_csv("data/model_fitted_params.csv", show_col_types = F)
mpx     <- read_csv("data/MPX_DGE.csv", show_col_types = F)
mrun    <- read_csv("data/model_summary.csv", show_col_types = F)
mqlow   <- read_csv("data/model_summary_qlow.csv", show_col_types = F)
mqhigh  <- read_csv("data/model_summary_qhigh.csv", show_col_types = F)

mx <- mpx |>
    filter(Estado == "Ciudad de México") |>
    mutate(Fecha = min(Fecha_reporte) + weeks(0:(n() - 1)))

mrun <- mrun |> 
    mutate(type = "point") |>
    bind_rows(
      mqlow |> mutate(type = "qlow")
    ) |>
    bind_rows(
      mqhigh |> mutate(type = "qhigh")
    ) 
    
columnames <- c("t", "S","E","I","R","V","PSS","PSE","PSI","PSR","PSV",
                      "PEE","PEI","PER","PEV","PII","PIR","PIV","PRR","PRV","PVV",
                      "C","Type")
colnames(mrun) <- columnames
  
mrun <- mrun |> 
    group_by(Type) |>
    arrange(t) |>
    mutate(Incidence = C - lag(C, default = 0)) |>
    ungroup() |>
    mutate(Fecha = min(mx$Fecha_reporte) + days(round(7*t)))
  
mrun <- mrun |>
    pivot_wider(id_cols = c(t,Fecha), names_from = Type, values_from = c(S:C,Incidence)) 

high <-  list.files("simulations", "model_sims_high.*.csv",
                   full.names = TRUE) |>
  read_csv(id = "nu", show_col_types = F) |>
  mutate(nu = str_remove_all(nu, ".*/model_sims_high|.csv")) |>
  mutate(nu = as.numeric(nu)) |>
  mutate(type = "high")

low  <-  list.files("simulations", "model_sims_low.*.csv",
                   full.names = TRUE) |>
  read_csv(id = "nu", show_col_types = F) |>
  mutate(nu = str_remove_all(nu, ".*/model_sims_low|.csv")) |>
  mutate(nu = as.numeric(nu)) |>
  mutate(type = "low")

point <-  list.files("simulations", "model_sims_low.*.csv",
                   full.names = TRUE) |>
  read_csv(id = "nu", show_col_types = F) |>
  mutate(nu = str_remove_all(nu, ".*/model_sims_low|.csv")) |>
  mutate(nu = as.numeric(nu)) |>
  mutate(type = "point")

point <- point %>%
  bind_rows(high) %>%
  bind_rows(low)

colnames(point) <- c("nu", columnames)

point <- point |> 
    group_by(Type) |>
    arrange(t) |>
    mutate(Incidence = C - lag(C, default = 0)) |>
    ungroup() |>
    mutate(Fecha = min(mx$Fecha_reporte) + days(round(7*t)))
  
point <- point |>
    pivot_wider(id_cols = c(nu,t,Fecha), names_from = Type, values_from = c(S:C,Incidence)) 

point <- point |>
  mutate(nufactor = factor(round(nu,3), ordered = TRUE)) |>
  mutate(nufactor = fct_recode(nufactor, "No vaccination" = "0"))

```

By `r format(today(), "%B %d %Y")` a total of `r sum(mx$Incidencia, na.rm = T)` cases have been reported for Mexico City. @fig-model-incidence shows the reported number of incident cases as well as the inferred number of total incident cases in the city. The average probability of detection was `r scales::percent(mean(mparam$p_detect), 0.01)` with 95% credible interval `r paste0("[", scales::percent(quantile(mparam$p_detect, probs = 0.025), 0.01), ", ", scales::percent(quantile(mparam$p_detect, probs = 0.975), 0.01),"]")`. Under the current scenario the epidemic is expected to extinguish by `r format(max(mrun$Fecha), "%B %d %Y")` with a total of `r paste0(round(max(mrun$C_point))," [",round(max(mrun$C_qlow)), ",", round(max(mrun$C_qhigh)),"]")` cumulative cases. 

```{r}
#| label: fig-model-incidence
#| message: false
#| warning: false
#| fig-height: 8.5
#| fig-width: 20
#| echo: false
#| out-width: 100%
#| fig-align: center
#| fig-cap: "Expected and observed number of MPX cases in Mexico City"

file_model <- "images/incidence.svg"
if (!file.exists(file_model) | remake_plots){
  
  inc_plot <- ggplot() +
    geom_ribbon(aes(x = Fecha, ymin = C_qlow, ymax = C_qhigh,
                    fill = "Model"),
                    alpha = 0.5, data = mrun) +
    geom_col(aes(x = Fecha, y = Casos, 
                  fill = "Observed"), size = 4, data = mx) +
    geom_text(aes(x = Fecha, y = Casos, label = Casos,
                  color = "Observed"), size = 4, data = mx, vjust = 0) +
    geom_line(aes(x = Fecha, y = C_point, color = "Model"), data = mrun,
              linetype = "dotted") +
    geom_line(aes(x = Fecha, y = C_qlow, color = "Model"), data = mrun,
              linetype = "dotted") +
    geom_line(aes(x = Fecha, y = C_qhigh, color = "Model"), data = mrun,
              linetype = "dotted") +
    theme_classic() +
    labs(
      y = "Cases",
      x = NULL,
      title = "Cumulative number of monkeypox cases in Mexico City",
      caption = "Cases reported by the General Directorate of Epidemiology | Bayesian pair-formation model"
    ) +
    scale_color_manual("Data", 
                       values = c("Model" = "#7e9bed","Observed" = "#d74f7c")) +
    scale_fill_manual("Data", 
                       values = c("Model" = "#7e9bed","Observed" = "#d74f7c")) +
    scale_y_continuous(labels = scales::comma) +
    coord_cartesian(xlim = c(min(mx$Fecha_reporte), max(mx$Fecha_reporte))) +
    scale_x_date(date_breaks = "1 week", date_labels = "%b-%d") +
    theme(
      plot.caption =  element_text(face = "italic", hjust = 1.0),
      plot.title = element_text(hjust = 0.5, size = 20)
    )
  ggsave(file_model, inc_plot, width = 10, height = 6)
}

knitr::include_graphics(file_model)  
```

```{r}
maxvac <- point %>%
  filter(Fecha == max(Fecha) & nu == max(nu))
```

@fig-model-vaccination-rates shows the different outcomes of cumulative cases under different vaccination rates $\nu$. With vaccination, the overall cases would reduce up to `r paste0(round(max(maxvac$C_point))," [",round(max(maxvac$C_low)), ",", round(max(maxvac$C_high)),"]")`. 

```{r}
#| label: fig-model-vaccination-rates
#| message: false
#| warning: false
#| fig-height: 8.5
#| fig-width: 20
#| echo: false
#| out-width: 100%
#| fig-align: center
#| fig-cap: "Expected outcomes according to different vaccination rates $\\nu$ in Mexico City"

file_model <- "images/vaccination_rates.svg"
if (!file.exists(file_model) | remake_plots){
  
  pcolor <- colorRampPalette(c("#7e9bed","#d74f7c"))
  vacplot <- ggplot(point) +
    geom_line(aes(x = Fecha, y = C_point, color = nufactor)) +
    geom_text(aes(x = Fecha, y = C_point,
                  label = glue("{round(C_point)} [{round(C_low)}, {round(C_high)}]"),
                  color = nufactor),  
              hjust = 0, size = 1.5,
              data = point %>% filter(Fecha == max(Fecha))) +
    theme_classic() +
    labs(
      y = "Cases",
      x = NULL,
      title = "Cumulative number of monkeypox cases in Mexico City under different vaccination rates",
      caption = "Cases reported by the General Directorate of Epidemiology | Bayesian pair-formation model"
    ) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_date(date_breaks = "1 week", date_labels = "%b-%d") +
    theme(
      plot.caption =  element_text(face = "italic", hjust = 1.0),
      plot.title = element_text(hjust = 0.5, size = 12),
      legend.position = "bottom"
    )  +
    coord_cartesian(xlim = c(min(point$Fecha), max(point$Fecha) + weeks(1))) +
    scale_color_manual("Vaccination rate", values = pcolor(length(unique(point$nu)))) +
    guides(col = guide_legend(nrow = 2))

  ggsave(file_model, vacplot, width = 8, height = 6)
}

knitr::include_graphics(file_model)  
```

## Discussion

Even under a small vaccination rate, the model shows a potential reduction in overall monkeypox cases in Mexico City. 


## References 

::: {#refs}
:::



## Model {#sec-diffeq .appendix} 

The compartmental diagram of the model is the following: 

```{r}
#| label: fig-diagram-model
#| message: false
#| warning: false
#| fig-height: 8.5
#| fig-width: 20
#| echo: false
#| out-width: 100%
#| fig-align: center
#| fig-cap: "Diagram of the model. Bright red node $P_{SI}$ is the main driver of the infection as it represents a partnership between a Susceptible and an Infected individual. This partnership irradiates the infection towards $P_{EI}$ if the susceptible becomes infected and the partnership continues. The partnership might also dissolve into the susceptible $S$ and the infected $I$ or might not result in an infection but a recovery of the infected partner $P_{SR}$."
set.seed(2456)
file_model <- "images/model_diagram.svg"
if (!file.exists(file_model) | remake_plots){
  dag_coords <-
    tibble(
      name = c("S", "E", "I", "R", "V", "PSS", "PSE", "PSI", "PSR", "PSV",
               "PEE", "PEI", "PER", "PEV","PII","PIR","PIV","PRR","PRV","PVV"),
      x    = c(1:5, 1,1.1,1.2,1.3,1.4,2.1,2.2,2.3,2.4,3.1,3.2,3.3,4.1,4.2,5.1),
      y    = c(rep(1.5, 5), c(1.3,1.2,1.1,1,0.9),c(1.3,1.2,1.1,1,0.9),c(1.3,1.2,1.1,1,0.9))
    )
  
  # save our DAG
  dagplot <- dagify(S ~ PSS,
         S ~ PSE,
         S ~ PSI,
         S ~ PSV,
         S ~ PSR,
         E ~ PSE,
         E ~ PEE,
         E ~ PEI,
         E ~ PER,
         E ~ PEV,
         I ~ PSI,
         I ~ PEI,
         I ~ PII,
         I ~ PIR,
         I ~ PIV,
         V ~ S,
         V ~ PSV,
         V ~ PEV,
         V ~ PIV,
         V ~ PRV,
         V ~ PVV,
         PSS ~ S,
         PSE ~ E,
         PSE ~ S,
         PSI ~ PSE,
         PSI ~ S,
         PSI ~ I,
         PSR ~ R,
         PSR ~ S,
         PSV ~ S,
         PSV ~ V,
         PSV ~ PSS,
         PEE ~ E,
         PEI ~ E,
         PEI ~ I,
         PEI ~ PSI,
         PEI ~ PEE,
         PER ~ PEI,
         PER ~ E,
         PER ~ R,
         PEV ~ V,
         PEV ~ E,
         PEV ~ PSE,
         PII ~ I,
         PII ~ PEI,
         PIV ~ PSI,
         PIV ~ PEV,
         PIV ~ I,
         PIV ~ V,
         PIR ~ I,
         PIR ~ R,
         PIR ~ PII,
         PRR ~ PIR,
         PRR ~ R,
         PRV ~ R,
         PRV ~ V,
         PRV ~ PSR,
         PRV ~ PIV,
         PVV ~ PSV,
         PVV ~ V
         ) %>% 
    tidy_dagitty() %>% 
    mutate(colour = case_when(
      str_detect(name, "PSI") ~ "#d74f7c",
      str_detect(to, "PSI")   ~ "#d74f7c",
      str_detect(name, "V") ~ "#7e9bed",
      str_detect(to, "V")   ~ "#7e9bed",
      TRUE ~ "#45485c"
    )) |>
    mutate(colpoint = if_else(str_detect(name,"PSI"),"A","B")) |>
    mutate(colpoint = if_else(str_detect(name,"V"),"C", colpoint)) |>
    ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_dag_node(aes(colour = colpoint)) +
    geom_dag_edges_diagonal(edge_alpha = 1, aes(edge_colour = colour)) +  
    geom_dag_text(size = 3) +
    theme_dag() +
    theme(
      legend.position = "none"
    ) +
    scale_color_manual(values = c("#d74f7c","#45485c","#7e9bed"))
  ggsave(file_model, dagplot, width = 20, height = 8.5)
} 

knitr::include_graphics(file_model)
```

Where the variables are specified in @tbl-variables.

| Variable    | Definition |
|-------------|---------------------------------------|
| $S$         | **Single** susceptible individuals    |
| $E$         | **Single** exposed individuals        |
| $I$         | **Single** infected individuals       |
| $R$         | **Single** recovered individuals      |
| $V$         | **Single** vaccinated individuals     |
| $P_{kl}$    | **Partnership** of two individuals in which one partner belongs to category $k$ and the other to category $l$ (_e.g._ $P_{SI}$ represents a partnership between a susceptible $S$ and an infected $I$ individual).  |
| $C$         | **Overall** cummulative infective cases. Total numner of infective cases independent of partnership status over all of the pandemic  |
| $T$         | **Overall** total infective cases. Total number of infective cases at a moment in time. Independent of partnership status.  |
| $\textrm{Inc}$ | **Overall** incident cases. New cases independent of  partnership status. |

: Variables used in the model @eq-model. {#tbl-variables}

The differential equation representation is given by:

$$
\begin{align}
\frac{dS}{dt}      &= -(\rho + \nu) S + \sigma (2 P_{SS} + P_{SE} + P_{SI} + P_{SR} + P_{SV})\\
\frac{dE}{dt}      &= -(\rho + \theta) E + \sigma (P_{SE} + 2 P_{EE} + P_{EI} + P_{ER} + P_{EV})\\
\frac{dI}{dt}      &= -(\rho + \delta) I + \theta E + \sigma (P_{SI} + P_{EI} + 2P_{II} + P_{IR} + P_{IV})  \\
\frac{dR}{dt}      &= - \rho R + \delta I + \sigma (P_{SR} + P_{ER} + P_{IR} + 2 P_{RR} + P_{RV})  \\
\frac{dV}{dt}      &= - \rho V + \nu S  + \sigma (P_{SV} + P_{EV} + P_{IV} + P_{RV} + 2 P_{VV})  \\
\frac{dP_{SS}}{dt} &= \frac{1}{2}\rho \frac{S^2}{N} - (\sigma + 2 \nu) P_{SS} \\
\frac{dP_{SE}}{dt} &= \rho \frac{SE}{N} - (\sigma + \theta + \nu) P_{SE} \\
\frac{dP_{SI}}{dt} &= \rho (1 - h) \frac{SI}{N} + \theta P_{SE} - (\sigma + \phi h + \delta + \nu) P_{SI} \\
\frac{dP_{SR}}{dt} &= \rho \frac{SR}{N} + \delta P_{SI} - (\sigma  + \nu) P_{SR} \\
\frac{dP_{SV}}{dt} &= \rho \frac{SV}{N} + \nu P_{SS} - (\sigma  + \nu) P_{SV} \\
\frac{dP_{EE}}{dt} &= \frac{1}{2} \rho \frac{E^2}{N} - (\sigma + 2 \theta) P_{EE} \\
\frac{dP_{EI}}{dt} &= \rho \frac{EI}{N} + \rho h \frac{SI}{N}  + \phi h P_{SI} + \theta P_{EE} - (\sigma + \theta + \delta) P_{EI} \\
\frac{dP_{ER}}{dt} &= \rho \frac{ER}{N} + \delta P_{EI} - (\sigma + \theta) P_{ER} \\
\frac{dP_{EV}}{dt} &= \rho \frac{EV}{N} + \nu P_{SE} - (\sigma + \theta) P_{EV} \\
\frac{dP_{II}}{dt} &= \frac{1}{2} \rho \frac{I^2}{N} + \theta P_{EI} - (\sigma + 2 \delta) P_{II} \\
\frac{dP_{IR}}{dt} &= \rho \frac{IR}{N} + \delta P_{II} + \theta P_{ER} - (\sigma + \delta) P_{IR} \\
\frac{dP_{IV}}{dt} &= \rho \frac{IV}{N} + \theta P_{EV} + \nu P_{SI} - (\sigma + \delta) P_{IV} \\
\frac{dP_{RR}}{dt} &= \frac{1}{2} \rho \frac{R^2}{N} + \delta P_{IR} - \sigma P_{RR} \\
\frac{dP_{RV}}{dt} &= \rho \frac{RV}{N} + \delta P_{IV} + \nu P_{SR} - \sigma P_{RV} \\
\frac{dP_{VV}}{dt} &= \frac{1}{2} \rho \frac{V^2}{N} + \nu P_{SV}  - \sigma  P_{VV} \\
\end{align}
$$ {#eq-model}
where $N = S + E + I + R + V + \sum_{i,j\in\{S,E,I,R,V\}} P_{ij}$ represents the total number of individuals (MSM) in the population. Initial conditions for the model are given by:

$$
\begin{align}
S(0) &= (N - \tilde{i}_w)\cdot p_{s},\\
I(0) &= \tilde{i}_w \cdot p_i,\\
P_{SS}(0) &= (N - \tilde{i}_w)\cdot (1 - p_{s}) \\
P_{SI}(0) &= (N - \tilde{i}_w)\cdot (1 - p_{i}) 
\end{align}
$$
with $\tilde{i_w} = i_w / p_{\text{detect}}$. The rest of the initial values are equal to zero. 


The parameters and their definitions are established in @tbl-parameters. 

| Parameter | Definition                              |
|-----------|-----------------------------------------|
| $\rho$    | Partnership formation rate.              |
| $\sigma$  | Partnership dissolution rate.            |
| $\nu$     | Vaccination rate.                        |
| $\theta$  | Incubation rate.                         |
| $\delta$  | Infection recovery rate.                 |
| $h$       | Probability of transmission per contact. |
| $\phi$    | Contact rate per partnership.            |
| $\varphi$ | Precision of the observed incidence cases.  |
| $p_{detect}$ | Probability of being a detected case.  |
| $N$       | The total of MSM in Mexico City           |
| $p_{s}$   | The proportion of **single** susceptible cases at the beginning of the epidemic. |
| $p_{i}$   | The proportion of **single** infected cases at the beginning of the epidemic.    |

: Parameters used in the model @eq-model. {#tbl-parameters}

The total number of infected individuals at any time $t$ can be estimated as:

$$
T = I + P_{SI} + P_{EI} + 2\cdot P_{II} + P_{IR} + P_{IV},
$${#eq-total}
and the cumulative number of infected individuals (cumulative cases) is given by the solution to the differential equation:

$$
\frac{dC}{dt} = \theta \cdot (E + P_{SE} + P_{EE} + P_{EI} + P_{ER} + P_{EV}).
$${#eq-cumcases}

The number of incident cases at week $w$, $\textrm{Inc}(w)$ is given by the difference in cumulative cases [@eq-cumcases]:

$$
\textrm{Inc}(w) = C(w+1) - C(w).
$$


## Parameter distributions {#sec-diffeq .appendix} 

```{r}
file_model <- "images/params_dist.svg"
if (!file.exists(file_model) | remake_plots){
  modelparams <- mparam |>
    select(iteration, chain, ρ:φ) |>
    pivot_longer(cols = ρ:φ, names_to = "Parameter") |>
    ggplot() +
    geom_density(aes(x = value, fill = Parameter)) +
    facet_wrap(~Parameter, scale = "free") +
    theme_minimal() +
    labs(
      x = "",
      y = "Density",
      title = "Inferred parameter distribution"
    ) +
    theme(legend.position = "none",
          plot.title = element_text(hjust = 0.5)) +
    scale_fill_manual("",
                       values = c("#003f5c","#0e4c70","#1e5984","#2e6699","#4074ae",
"#5381c3","#688ed8","#7e9bed","#575e83","#45485c"))
  ggsave("images/parameters.svg", modelparams, width = 8, height = 4)
}
knitr::include_graphics("images/parameters.svg")
```